---
title: "Assignment-5-Problem-4"
author: "Laura Ingulsrud"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
FacultySalary<-read.csv("Faculty salary data (2008 - 2009 survey).csv")

```

4) Exploring academic salaries for professors in U.S. colleges. Explore relationships between
variables in the ‘Faculty salary data (2008 - 2009 survey)’ dataset. Develop a model describing faculty salary based on data for faculty sex, rank, years in current position, field, and number of years since doctoral degree was earned. You should make decisions regarding which variables should remain in your final model. Describe the results qualitatively and quantitatively (i.e., don’t just report the statistical results of the model – make sure you describe interesting findings in text). You can also discuss any concerns that you have with the model(s) you present, if any.

```{r}
# regression! 
salary_lm1<- lm(Salary~ YearsPhD + FacultyRank+ YearsFaculty + Sex + Discipline, data = FacultySalary)
salary_lm1

# the Questions says I should maked decisions aboutwhich variables to keep but, I think it makes sense to keep all?

# b. Model summary:
summary(salary_lm1)
```

